---
title: "CLIAR Data Report: `r params$family`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document: default
  word_document:
    reference_docx: reference_landscape.docx
params:
  output_type: html
  family: NULL
  ref_year: NULL
  variables: NULL
  coverage: NULL
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
is_html <- identical(params$output_type, "html")
```

```{css, echo = FALSE, eval = is_html}
.main-container { max-width: 1400px; }
.table-scroll { overflow-x: auto; }
```

This report documents the `r nrow(params$variables)` indicators of the
**`r params$family`** institutional family and their data coverage, with
`r params$ref_year` as the reference year.

# Variables

```{r variables}
# column widths in inches; landscape Letter leaves ~9.5in between margins
flextable::flextable(params$variables) |>
  flextable::width(
    j     = c("Variable", "Name", "Definition", "Source"),
    width = c(1.7, 2.0, 3.8, 2.0)
  ) |>
  flextable::fontsize(size = 9, part = "all") |>
  flextable::valign(valign = "top", part = "body") |>
  flextable::theme_vanilla()
```

# Coverage

Coverage statistics are computed with `cliaretl::compute_coverage()`. Flags
equal to 1 indicate that the criterion is met:

- **Flag Continuity**: at least one observation in the five years before the reference year.
- **Flag Country Coverage**: in the last five years, at least 100 countries, or at least 50 countries spanning all 7 regions.
- **Flag Year Coverage**: at least two years with 10 or more countries each.
- **Static / Dynamic Valid Years**: years with 10 or more countries within the static window or the dynamic panel.

::: {.table-scroll}
```{r coverage}
knitr::kable(params$coverage)
```
:::
